Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-21 ind_files/02_math_background.tex
Minor rephrasing

for two `nice' real functions $f$ and $g$, then, given any real function $h$, we can calculate how the quantity $h(x)$ changes using the chain rule of differentiation, which says that

>>>>

for two `nice' real functions $f$ and $g$, then, given any real function $h$, we can calculate how the quantity $h(x(t))$ changes over time using the chain rule of differentiation, which says that
